The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-28 paper.tex
update

  The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{pc}^{3}$ is\
  much smaller than that of individual clump by a factor of 83.\
  By intentionally reducing the volume ratio of the jet source to an individual clump,\
  we can diminish the effect of the randomness of the clumps on the bubbles.

>>>>

  The bipolar jets are constantly and bidirectionally ejected from a cylindrical source\
  with diameter and height of 4 pc, leading to the source volume $\sim 50 \text{ pc}^{3}$ is\
  much smaller than that of individual clump by a factor of 83.\
  By intentionally reducing the volume ratio of the jet source to an individual clump,\
  we can diminish the effect of the randomness of the clumps on the bubbles.
